%%% The main file. It contains definitions of basic parameters and includes all other parts.

%% Settings for single-side (simplex) printing
% Margins: left 40mm, right 25mm, top and bottom 25mm
% (but beware, LaTeX adds 1in implicitly)
\documentclass[12pt,a4paper]{report}
\setlength\textwidth{145mm}
\setlength\textheight{247mm}
\setlength\oddsidemargin{15mm}
\setlength\evensidemargin{15mm}
\setlength\topmargin{0mm}
\setlength\headsep{0mm}
\setlength\headheight{0mm}
% \openright makes the following text appear on a right-hand page
\let\openright=\clearpage

%% Settings for two-sided (duplex) printing
% \documentclass[12pt,a4paper,twoside,openright]{report}
% \setlength\textwidth{145mm}
% \setlength\textheight{247mm}
% \setlength\oddsidemargin{14.2mm}
% \setlength\evensidemargin{0mm}
% \setlength\topmargin{0mm}
% \setlength\headsep{0mm}
% \setlength\headheight{0mm}
% \let\openright=\cleardoublepage

%% Generate PDF/A-2u
\usepackage[a-2u]{pdfx}

%% Character encoding: usually latin2, cp1250 or utf8:
\usepackage[utf8]{inputenc}

%% Prefer Latin Modern fonts
\usepackage{lmodern}

%% Further useful packages (included in most LaTeX distributions)
\usepackage{amsmath}           % extensions for typesetting of math
\usepackage{amsfonts}          % math fonts
\usepackage{amsthm}            % theorems, definitions, etc.
\usepackage{bbding}            % various symbols (squares, asterisks, ...)
\usepackage{bm}                % boldface symbols (\bm)
\usepackage{graphicx}          % embedding of pictures
\usepackage{fancyvrb}          % improved verbatim environment
\usepackage[square]{natbib}            % citation style AUTHOR (YEAR), or AUTHOR [NUMBER]
\usepackage[nottoc]{tocbibind} % makes sure that bibliography and the lists
                               % of figures/tables are included in the table
                               % of contents
\usepackage{dcolumn}           % improved alignment of table columns
\usepackage{booktabs}          % improved horizontal lines in tables
\usepackage{paralist}          % improved enumerate and itemize
\usepackage{xcolor}            % typesetting in color
\usepackage{xurl}
\usepackage{hyperref}
\usepackage{nameref}
\usepackage{macros}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage[capitalise]{cleveref}
\usepackage{tikz}
\usepackage{siunitx}
\usetikzlibrary{positioning, graphs, arrows.meta, calc, quotes}
\usepackage[nohyperlinks]{acronym}


\tikzset{process/.style={
    rectangle,
    rounded corners=3mm,
    minimum size=6mm,
    top color=blue!10,
    bottom color=blue!30,
    font=\footnotesize
}}
\tikzset{data/.style={
    rectangle,
    fill=green!20,
    minimum size=6mm,
    align=left,
    font=\footnotesize
}}
\definecolor{darkgreen}{RGB}{0,100,0}


%%% Basic information on the thesis

% Thesis title in English (exactly as in the formal assignment)
\def\ThesisTitle{Evaluating Point Cloud Rendering Approaches for Camera Pose Verification}
\def\NazevPrace{Použití metod zobrazení mračna bodů pro ověření polohy kamery}

% Author of the thesis
\def\ThesisAuthor{Tomáš Kremel}

% Year when the thesis is submitted
\def\YearSubmitted{2024}

% Name of the department or institute, where the work was officially assigned
% (according to the Organizational Structure of MFF UK in English,
% or a full name of a department outside MFF)
\def\Department{Department of Software and Computer Science Education}
\def\Katedra{Katedra softwaru a výuky informatiky}

% Department of Theoretical Computer Science and Mathematical Logic
% Is it a department (katedra), or an institute (ústav)?
\def\DeptType{Department}
\def\TypPracoviste{Katedra}

% Thesis supervisor: name, surname and titles
\def\SupervisorA{doc. Ing. Tomáš Pajdla, Ph.D.}
\def\SupervisorB{Torsten Sattler, Dr. rer. nat.}

% Supervisor's department (again according to Organizational structure of MFF)
\def\SupervisorsDepartment{Department of Algebra}
\def\KatedraVedouciho{Katedra algebry}

% Study programme and specialization
\def\StudyProgramme{Computer Science}
\def\StudyBranch{Artificial Intelligence}

% An optional dedication: you can thank whomever you wish (your supervisor,
% consultant, a person who lent the software, etc.)
\def\Dedication{%
I would like to express my gratitude and appreciation to my supervisors,
for their suggestions, great support, and inexhaustible patience while
I was finding motivation to put this work into reality. I would also like
to thank The Czech Institute of Informatics, Robotics, and Cybernetics
(CIIRC) for providing me with all the
necessary GPU resources required for computations. Further, I would like
to recognize my friends Tomáš Souček and Vojtěch Kužel for their consultations.
Finally, the credit goes to Sára Filípková, without whom this thesis
would not be a reality.
}

% Abstract (recommended length around 80-200 words; this is not a copy of your thesis assignment!)
\def\Abstract{%
Visual localization is the problem of estimating the 6~degrees of freedom
camera pose from which a query image was taken relative to a known
reference scene representation. It is the key for applications such as
Augmented, Mixed, and Virtual Reality, as well as autonomous robotics
such as drones or self-driving cars.

This thesis focuses on a visual localization pipeline, especially on
its pose verification and reranking step. The pipeline uses 3D point clouds
and 2D-3D correspondences between the query image and 3D scene points for
candidate camera poses estimations. The thesis explores point cloud
rendering approaches as they are utilized in the pipeline and the
verification step---the render of the discretized scene from a given
candidate position is compared to the actual query image to asses if the
given couple depicts the same place.

One of the main challenges of such rendering is occlusion handling. Due
to the sparsity of points employed for otherwise continuous real world
representation, information about what lies in the front and what is
hidden can be easily lost when projected to the 2D image. Rendering
approaches explored in this thesis focus on the challenge directly or
as a component of a novel view synthesis DNN-based renderer.
Rendering influence on localization performance is investigated.
}

% 3 to 5 keywords (recommended), each enclosed in curly braces
\def\Keywords{%
{point clouds,} {rendering,} {neural rendering,} {localization}
}

\def\Abstrakt{%
Vizuální lokalizace je problém odhadování parametrů šesti stupňů volnosti
pozice kamery, z~níž byla pořízena dotazovaná fotografie, přičemž pozice
je vztažena ke známé reprezentaci referenčního prostředí. Řešení tohoto
problému je klíčové v~aplikacích jako jsou rozšířená, smíšená a~virtuální
realita, stejně tak v~oblasti autonomní robotiky zahrnující drony
a~samořiditelné automobily.

Tato práce se soustředí na vizuální lokalizačního algoritmus, zejména na
jeho verifikační a~přeřazovací krok. Tento algoritmus interně využívá
tří dimenzionální mračna bodů a~hledání korespondencí mezi těmito body
a~dotazovanou fotografií pro nalezení odhadů kandidátních pozic kamery.
Práce zkoumá přístupy k~renderování mračen bodů a jejich využití v~rámci
algoritmu a jeho verifikačního kroku~-- render diskretizovaného prostředí
z~konkrétní kandidátní pozice se v něm porovnává s~danou dotazovanou fotografií
za účelem určení toho, zda oba pohledy zobrazují to samé místo.

Jedna z~hlavních výzev renderingu diskretizovaného prostředí jsou okluze.
Kvůli řídkosti bodů využitých jako reprezentace jinak spojitého reálného
světa může být informace o~tom co leží v~popředí a co v~pozadí lehce
ztracena při promítnutí bodů na dvou dimenzionální obraz. Přístupy
k~renderování zkoumané v~této práci se soustředí na renderování bodů přímo
nebo jako komponentu rendereru \uv{nových pohledů} využívající hlubokých
neuronových sítí. Je zde prověřen vliv těchto renderovacích přístupů na
přesnost lokalizace.
}

\def\KlicovaSlova{%
{mračna bodů,} {rendering,} {neurální rendering,} {lokalizace}
}

%% The hyperref package for clickable links in PDF and also for storing
%% metadata to PDF (including the table of contents).
%% Most settings are pre-set by the pdfx package.
\hypersetup{unicode}
\hypersetup{breaklinks=true}

% Definitions of macros (see description inside)
% \include{macros}

% Title page and various mandatory informational pages
\begin{document}
\include{title}

%%% A page with automatically generated table of contents of the master thesis

\tableofcontents

%% Each chapter is kept in a separate file
\include{chap_0.0.0_Introduction}
\include{chap_1.0.0_Visual_Localization}
\include{chap_2.0.0_Pointcloud_Rendering}
\include{chap_3.0.0_Pose_Verification}
\include{chap_3.1.0_Datasets}
\include{chap_3.2.0_Implementation}
\include{chap_3.3.0_Experiments}
\include{chap_4.0.0_Conclusion}

%%% Bibliography
\include{bibliography}

%%% Figures used in the thesis (consider if this is needed)
\listoffigures

%%% Tables used in the thesis (consider if this is needed)
%%% In mathematical theses, it could be better to move the list of tables to the beginning of the thesis.
\listoftables

%%% Abbreviations used in the thesis, if any, including their explanation
%%% In mathematical theses, it could be better to move the list of abbreviations to the beginning of the thesis.
\chapwithtoc{List of Abbreviations}
\begin{acronym}
 \acro{CG}{Computer Graphics}
 \acro{CNN}{Convolutional Neural Network}
 \acro{CSG}{Constructive Solid Geometry}
 \acro{CV}{Computer Vision}
 \acro{DB}{Database}
 \acro{DNN}{Deep Neural Network}
 \acro{EWA}{Elliptical Weighted Average}
 \acro{FoV}{Field of View}
 \acro{GAN}{Generative Adversarial Networks}
 \acro{GPU}{Graphics Processing Unit}
 \acro{IMC}{Image Matching Challenge}
 \acro{MVS}{MultiView Stereo}
 \acro{NN}{Neural Network}
 \acro{NRIW}{Neural Rerendering in the Wild}
 \acro{OS}{Operating System}
 \acro{RGB(D)}{Red Green Blue (Depth)}
 \acro{SDF}{Signed Distance Functions}
 \acro{SfM}{Structure from Motion}
 \acro{VAE}{Variational Autoencoder}
 \acro{VGG}{Visual Geometry Group}
\end{acronym}

%%% Attachments to the master thesis, if any. Each attachment must be
%%% referred to at least once from the text of the thesis. Attachments
%%% are numbered.
%%%
%%% The printed version should preferably contain attachments, which can be
%%% read (additional tables and charts, supplementary text, examples of
%%% program output, etc.). The electronic version is more suited for attachments
%%% which will likely be used in an electronic form rather than read (program
%%% source code, data files, interactive charts, etc.). Electronic attachments
%%% should be uploaded to SIS and optionally also included in the thesis on a~CD/DVD.
%%% Allowed file formats are specified in provision of the rector no. 72/2017.
%\appendix
%\chapter{Attachments}

%\section{First Attachment}

\openright
\end{document}
